---
title: "Analyse COVID data"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# setup environment
library(haven)      # For importing SPSS data
library(readxl)     # For reading excel files
library(plyr)       # Data wrangling
library(dplyr)      # Data wrangling improved
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(magrittr)   # Pipes in R
library(lme4)       # linear mixed effects models
library(broom.mixed)# tidy and glance models for mixed effects classes
library(purrr)      # functional programming
```

---

# Read in the imputed data
```{r cache = TRUE}
imp <- readRDS("imp_20it.RDS")
```

---

# Make into long format
```{r cache = TRUE}
long <- mice::complete(imp, "long", include = TRUE)
```

---

# Post-processing the imputations

## Combine smaller household categories into one 'other'
```{r cache = TRUE}
long$q29[long$q29 == 6] <- 5
long$q29[long$q29 == 7] <- 5
long <- long %>% mutate(
  q29 = as.factor(q29)
)
levels(long$q29)<- c("Alleenstaand zonder kinderen", 
                     "Alleenstaand met kinderen", 
                     "Samenwonend met partner met thuiswonende kinderen",
                     "Samenwonend met partner zonder thuiswonende kinderen", 
                     "Anders")
```

## Combine education levels into three names categories
```{r cache = TRUE}
long$edu[long$edu < 4] <- 1
long$edu[long$edu == 4 | long$edu == 5] <- 2
long$edu[long$edu > 5] <- 3
long <- long %>% mutate(
  edu = as.factor(edu)
)
levels(long$edu)<- c("Hoog", "Middel", "Laag")
```

## Label factor levels for sex and ethnic background
```{r cache = TRUE}
long$sekse <- as.factor(long$sekse)
levels(long$sekse) <- c("Man", "Vrouw")
long$etn_herkomst <- as.factor(long$etn_herkomst)
levels(long$etn_herkomst)<- c("Nederlandse achtergrond", 
                              "Westerse migratieachtergrond", 
                              "Niet-westerse migratieachtergrond")
```

## Combine items of scale contructs into variables
```{r cache = TRUE}
long <- long %>% 
  mutate(onvr = rowMeans(select(., q48_1, q48_9, q48_10,  q48_11, q48_12), na.rm=TRUE), #onvrede met beleid
         drei = rowMeans(select(., q47_1, q47_2, q47_3), na.rm=TRUE), #dreiging ervaren
         rond = q59, #rondkomen
         gezo = q43,
         huis = q29) #gezondheid
```

---

## Calculate age
```{r cache = TRUE}
long <- long %>% mutate(
  age = 2020-geboortejaar
)
```

---

## Subset of columns
```{r cache = TRUE}
long_subset <- long %>% 
  select(.imp, 
         .id, 
         id, 
         meting_mnd, 
         meting_squared, 
         edu, 
         oesch, 
         age, 
         sekse, 
         etn_herkomst, 
         onvr, 
         drei, 
         rond, 
         gezo,
         q60_1,
         huis
         )
```


## Convert back to imputation object
```{r cache = TRUE}
imp_post <- as.mids(long_subset)
#save(imp_post, file = "./imputaties.RData")
```

---

# Analyses

---

## Analysis 1: Model with Time
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd +  (1|id))) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert

# report
results_vert[["estimates"]][,c(1, 2, 5)] %>% signif(., 3) 
```


---


## Analysis 2: Model with time-independent predictors added
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id))) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert

# report
results_vert[["estimates"]][,c(1, 2, 5)] %>% signif(., 3) 
```

---

## Analysis 3: Model with time-dependent predictors added
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id) + gezo + rond + drei + onvr)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## Analysis 4: Model with random effects for time added
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1 + meting_mnd | id) + gezo + rond  + drei + onvr)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## Analysis 5: Rerun the analysis with only the time-dependent deviations without random effect for `meting_mnd`
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %>% 
        group_by(meting_mnd) %>% 
        mutate(gezo_mean = mean(gezo, na.rm = TRUE), 
               gezo_dev = gezo - gezo_mean,
               rond_mean = mean(rond, na.rm = TRUE), 
               rond_dev = rond - rond_mean,
               drei_mean = mean(drei, na.rm = TRUE), 
               drei_dev = drei - drei_mean,
               onvr_mean = mean(onvr, na.rm = TRUE), 
               onvr_dev = onvr - onvr_mean) %>% 
        ungroup(meting_mnd) %$% 
        lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1 | id) + gezo_dev + rond_dev + drei_dev + onvr_dev)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## Analysis 6: Rerun the analysis with only the time-dependent deviations
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %>% 
        group_by(meting_mnd) %>% 
        mutate(gezo_mean = mean(gezo, na.rm = TRUE), 
               gezo_dev = gezo - gezo_mean,
               rond_mean = mean(rond, na.rm = TRUE), 
               rond_dev = rond - rond_mean,
               drei_mean = mean(drei, na.rm = TRUE), 
               drei_dev = drei - drei_mean,
               onvr_mean = mean(onvr, na.rm = TRUE), 
               onvr_dev = onvr - onvr_mean) %>% 
        ungroup(meting_mnd) %$% 
        lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1 + meting_mnd | id) + gezo_dev + rond_dev + drei_dev + onvr_dev)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

Random effect for time is not significant

---


# Additional  analysis 

---

## Analysis 7: Model with random effects for time added
But now  while enforcing a zero correlation between the intercept deviations and `meting_mnd` effect deviations across levels of `id`.
```{r cache = TRUE}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ (1 | id) +  meting_mnd + (0 + meting_mnd | id) + age + sekse + etn_herkomst + edu + huis + gezo + rond + drei + onvr)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## How is time coded
```{r}
imp_post$data$meting_mnd %>% table()
```

---

## Do time-dependent predictors have mean zero per time? 
For Analysis 3: NO
```{r}
imp_post %>% 
  complete("all") %>% 
  map(~.x %>% 
        select(meting_mnd, gezo, rond, drei, onvr) %>% 
        group_by(meting_mnd) %>% 
        summarise_all(.funs = mean)) %>% 
  Reduce("+", .) / imp_post$m
```
As per Analysis 5, Analysis 6 and Analysis 7, the deviations sums to 0
```{r}
imp_post %>% 
complete("all") %>% 
  map(~.x %>% 
        group_by(meting_mnd) %>% 
        mutate(gezo_mean = mean(gezo, na.rm = TRUE), 
               gezo_dev = gezo - gezo_mean,
               rond_mean = mean(rond, na.rm = TRUE), 
               rond_dev = rond - rond_mean,
               drei_mean = mean(drei, na.rm = TRUE), 
               drei_dev = drei - drei_mean,
               onvr_mean = mean(onvr, na.rm = TRUE), 
               onvr_dev = onvr - onvr_mean) %>% 
        select(meting_mnd, gezo_dev, rond_dev, drei_dev, onvr_dev) %>% 
  summarise_all(.funs = mean) %>% round(5)) %>% 
  Reduce("+", .) / imp_post$m
```
The means should be identical to those under Analysis 3
```{r}
imp_post %>% 
complete("all") %>% 
  map(~.x %>% 
        group_by(meting_mnd) %>% 
        mutate(gezo_mean = mean(gezo, na.rm = TRUE), 
               gezo_dev = gezo - gezo_mean,
               rond_mean = mean(rond, na.rm = TRUE), 
               rond_dev = rond - rond_mean,
               drei_mean = mean(drei, na.rm = TRUE), 
               drei_dev = drei - drei_mean,
               onvr_mean = mean(onvr, na.rm = TRUE), 
               onvr_dev = onvr - onvr_mean) %>% 
        select(meting_mnd, gezo_mean, rond_mean, drei_mean, onvr_mean) %>% 
  summarise_all(.funs = mean)) %>% 
  Reduce("+", .) / imp_post$m
```

---

## What about further (re)scaling because of non-convergence
Does not do much, in my opinion, as the correlations between the fixed effects are not large.
```{r}
fit[[1]] %>% summary() %>% print(correlation = TRUE)
```

---

## Correlations between vertrouwen (`q60_1`) and the calculated means per measurement occasion
```{r}
Means <- imp_post %>% 
  complete("all") %>% 
  map(~.x %>% 
        group_by(meting_mnd) %>% 
        mutate(gezo_mean = mean(gezo, na.rm = TRUE), 
               gezo_dev = gezo - gezo_mean,
               rond_mean = mean(rond, na.rm = TRUE), 
               rond_dev = rond - rond_mean,
               drei_mean = mean(drei, na.rm = TRUE), 
               drei_dev = drei - drei_mean,
               onvr_mean = mean(onvr, na.rm = TRUE), 
               onvr_dev = onvr - onvr_mean) %>% 
        select(q60_1, meting_mnd, gezo_mean, rond_mean,  drei_mean, onvr_mean) %>% 
        summarise_all(.funs = mean)) %>% 
  Reduce("+", .) / imp_post$m
Means
cor(Means)
```


