---
title: "Additional analyses"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: html_document
---

---
title: "Analyse COVID data"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# setup environment
library(haven)      # For importing SPSS data
library(readxl)     # For reading excel files
library(plyr)       # Data wrangling
library(dplyr)      # Data wrangling improved
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(magrittr)   # Pipes in R
library(lme4)       # linear mixed effects models
library(broom.mixed)# tidy and glance models for mixed effects classes
library(purrr)      # functional programming
```

---

# Read in the incomplete data

# Import the preprocessed incomplete data.
```{r data}
load("../Data/clean.Rdata")
```


# Post-processing the variables

Combine items of scale contructs into variables.
```{r cache = TRUE}
long <- dat_clean %>% 
  mutate(ment = rowMeans(select(., q49_1, q49_2, q49_3, q49_4, q49_5, q49_6), na.rm=TRUE), #mentale gevolgen
         econ = rowMeans(select(., q52, q53, q54), na.rm=TRUE),  #economische
         onvr = rowMeans(select(., q48_1, q48_9, q48_10,  q48_11, q48_12), na.rm=TRUE), #onvrede met beleid
         drei = rowMeans(select(., q47_1, q47_2, q47_3), na.rm=TRUE), #dreiging ervaren
         cont = rowMeans(select(., q33_1, q33_2, q33_3,  q33_4, q33_5, q33_6), na.rm=TRUE),  #sociaal contact
         eenz = rowMeans(select(., q34_1, q34_2, q34_3,  q34_4, q34_5), na.rm=TRUE), #eenzaamheid
         hulp = rowMeans(select(., q38_1, q38_2, q38_3,  q38_4), na.rm=TRUE), #hulp ontvangen
         medi = rowMeans(select(., q31_1, q31_2, q31_3,  q31_4, q31_5, q31_6, q31_7), na.rm=TRUE), #mediagebruik
         rond = q59, #rondkomen
         gezo = q43, #gezondheid
         huis = q29) #huishouden
```

Subset of columns.
```{r cache = TRUE}
long_subset <- long %>% 
  select(id, 
         meting_mnd, 
         meting_squared, 
         weegfactor,
         edu, 
         age, 
         sekse, 
         etn_herkomst, 
         ment, 
         econ, 
         onvr, 
         drei, 
         cont, 
         eenz, 
         hulp, 
         medi, 
         rond, 
         gezo,
         q60_1,
         huis
         )
```

Select rows.

```{r}
complete_cases <- long_subset[rowSums(is.na(long_subset)) == 0, ]
```

---

# Complete case analysis

---

Intercept-only model
```{r}
fit <- lme4::lmer(q60_1 ~ (1|id), complete_cases)
broom.mixed::tidy(fit)
```

```{r}
fit <- lme4::lmer(q60_1 ~ meting_mnd +  (1|id), complete_cases)
broom.mixed::tidy(fit)
```

```{r}
fit <- lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id), complete_cases)
broom.mixed::tidy(fit)
```