---
title: "Additional analyses"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: html_document
---

---
title: "Analyse COVID data"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# setup environment
library(haven)      # For importing SPSS data
library(readxl)     # For reading excel files
library(plyr)       # Data wrangling
library(dplyr)      # Data wrangling improved
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(magrittr)   # Pipes in R
library(lme4)       # linear mixed effects models
library(broom.mixed)# tidy and glance models for mixed effects classes
library(purrr)      # functional programming
library(tidyr)      # functional programming
```

---

# Read in the incomplete data

# Import the imputed data.
```{r}
imp <- readRDS("../Data/imp_20it.RDS")
long <- mice::complete(imp, "long", include = TRUE)
```

Load relevant variables.
```{r variables}
vars_outcome <- c("q60_1", "q49_1", "q49_2", "q49_3", "q49_4", "q49_5", "q49_6")
vars_fixed <- c("weegfactor", "edu", "age", "q29", "q52", "q53", "q54", "sekse", "etn_herkomst")
vars_random <- c("meting_mnd", "meting_squared", "q43", "q48_1", "q48_9", "q48_10", "q48_11", "q48_12", "q47_1", "q47_2", "q47_3", "q33_1", "q33_2", "q33_3", "q33_4", "q33_5", "q33_6")
vars_covariates <- c("q34_1", "q34_2", "q34_3", "q34_4", "q34_5", "q38_1", "q38_2", "q38_3", "q38_4", "q31_1", "q31_2", "q31_3", "q31_4", "q31_5", "q31_6", "q31_7", "q59", "q60_2", "q60_3", "q60_4", "q60_8", "q60_10", "q60_12")
vars_analyse <- c("id", vars_fixed, vars_outcome, vars_random)
```


# Post-processing the variables

Label factor levels.
```{r}
long <- long %>% mutate(
  q29 = as.factor(q29),
  edu = as.factor(edu),
  etn_herkomst = as.factor(etn_herkomst)
)
levels(long$q29)<- c("Alleenstaand_zonder-kinderen", 
                     "Alleenstaand_met_kinderen", 
                     "Samenwonend_met_partner_met_thuiswonende_kinderen",
                     "Samenwonend_met_partner_zonder_thuiswonende_kinderen", 
                     "Anders")
levels(long$edu)<- c("Hoog", "Middel", "Laag")
levels(long$etn_herkomst)<- c("Nederlandse_achtergrond", 
                              "Westerse_migratieachtergrond", 
                              "Niet_westerse_migratieachtergrond")
```


Combine items of scale contructs into variables.
```{r}
long <- long %>% 
  mutate(ment = rowMeans(select(., q49_1, q49_2, q49_3, q49_4, q49_5, q49_6), na.rm=TRUE), #mentale gevolgen
         econ = rowMeans(select(., q52, q53, q54), na.rm=TRUE),  #economische
         onvr = rowMeans(select(., q48_1, q48_9, q48_10,  q48_11, q48_12), na.rm=TRUE), #onvrede met beleid
         drei = rowMeans(select(., q47_1, q47_2, q47_3), na.rm=TRUE), #dreiging ervaren
         cont = rowMeans(select(., q33_1, q33_2, q33_3,  q33_4, q33_5, q33_6), na.rm=TRUE),  #sociaal contact
         eenz = rowMeans(select(., q34_1, q34_2, q34_3,  q34_4, q34_5), na.rm=TRUE), #eenzaamheid
         hulp = rowMeans(select(., q38_1, q38_2, q38_3,  q38_4), na.rm=TRUE), #hulp ontvangen
         medi = rowMeans(select(., q31_1, q31_2, q31_3,  q31_4, q31_5, q31_6, q31_7), na.rm=TRUE), #mediagebruik
         rond = q59, #rondkomen
         gezo = q43, #gezondheid
         huis = q29) #huishouden
long[sapply(long, is.nan)] <- NA 
```

Subset of columns.
```{r}
long_subset <- long %>% 
  select(.imp,
         .id,
         id, 
         meting_mnd, 
         meting_squared, 
         weegfactor,
         edu, 
         age, 
         sekse, 
         etn_herkomst, 
         ment, 
         econ, 
         onvr, 
         drei, 
         cont, 
         eenz, 
         hulp, 
         medi, 
         rond, 
         gezo,
         q60_1,
         huis
         )
```

## Convert back to imputation object
```{r }
imp_post <- as.mids(long_subset)
#save(imp_post, file = "./imputaties.RData")
```

---

# Weighted analysis

---

Re-run the analyses weighted by `weegfactor`.

## Analysis 1: Model with Time
```{r}
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd +  (1|id), weights = .x$weegfactor)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```


---


## Analysis 2: Model with time-independent predictors added
```{r }
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id), weights = .x$weegfactor)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## Analysis 3: Model with time-dependent predictors added
```{r }
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id) + gezo + rond + medi + hulp + eenz + cont + drei + onvr + econ + ment), weights = .x$weegfactor) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

# Complete case analysis

---


Select rows for complete case analysis.
```{r}
complete_cases <- long_subset[rowSums(is.na(long_subset)) == 0 & long_subset$.imp == 0, ]
```



Intercept-only model
```{r}
fit <- lme4::lmer(q60_1 ~ (1|id), complete_cases)
broom.mixed::tidy(fit)
```

```{r}
fit <- lme4::lmer(q60_1 ~ meting_mnd +  (1|id), complete_cases)
broom.mixed::tidy(fit)
```

```{r}
fit <- lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id), complete_cases)
broom.mixed::tidy(fit)
```

---

# Re-measured cases

---

The following code converts the data into 'wide format', where each row represents one respondent, and time-varying variables are repeated measurements over several columns. This allows us to evaluate the missing data pattern in the outcome variable (q60_1) over the time in months (q60_1m0 through q60_1m17).

```{r wide}
dat_wide <- imp$data %>% 
  pivot_wider(id_cols = c("id", all_of(vars_fixed)), values_from = c(vars_outcome, vars_random, vars_covariates), names_from = "meting_mnd", names_sep = "m")
plot_pattern(dat_wide[, c("id", "q60_1m0", "q60_1m3", "q60_1m7", "q60_1m12", "q60_1m17")], square = FALSE)
n_mis <- rowSums(is.na(dat_wide[, c("q60_1m0", "q60_1m3", "q60_1m7", "q60_1m12", "q60_1m17")]))
ids <- dat_wide[n_mis < 4, "id"]
```

Now we need to load the imputed data and select the cases with two or more measurements.
```{r}
dat_remeasured <- long_subset[long_subset$id %in% ids$id, ]
imp_post <- as.mids(dat_remeasured)
```

## Analysis 1: Model with Time
```{r }
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd +  (1|id))) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```


---


## Analysis 2: Model with time-independent predictors added
```{r }
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id))) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```

---

## Analysis 3: Model with time-dependent predictors added
```{r }
fit <- imp_post %>% 
  complete("all") %>% 
  map(~.x %$% lme4::lmer(q60_1 ~ meting_mnd + age + sekse + etn_herkomst + edu + huis + (1|id) + gezo + rond + medi + hulp + eenz + cont + drei + onvr + econ + ment)) 
# First imputed set
fit[[1]] %>% summary() %>% print(correlation = TRUE)
# Summary AIC
fit %>% map(~.x %>% AIC()) %>% unlist() %>% summary()
# Pooled imputations
fit %>% 
  pool() %>% 
  broom.mixed::tidy()
results_vert <- mitml::testEstimates(as.mitml.result(fit), extra.pars = TRUE)
results_vert
```



