---
title: "Imputatie COVID data"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# setup environment
library(haven)      # For importing SPSS data
library(readxl)     # For reading excel files
library(tidyverse)  # All things useful
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(plyr)       # Data wrangling
library(magrittr)   # Pipes in R

# Define function for `not in`
`%nin%` <- Negate(`%in%`)

# Function for the mode of a vector
modus <- function(x) {
  tally <- table(x, useNA = "no")
  if(dim(tally)==0) {
    mode <- NA
    } else {
      mode <- names(which.max(tally))
      }
  return(as.numeric(mode))
}

modus_per_column <- function(x) {
  apply(x, 2, modus)
}
```

---

# Import the data
```{r data}
dat_raw <- read_sav("data.zsav") %>% zap_labels()
```

---

# Data editing

---

## Rename and clean labels and attributes
```{r clean}
# clean names
dat_rename <- janitor::clean_names(dat_raw) 
# strip attributes
dat_rename[] <- lapply(dat_rename, as.vector)
vars <- names(dat_rename)
```

---

## Make time dimension consistent and add polynomial for measurement occasion
The following step adds non-observed measurement occasions when participants do not have all measurement occasions observed. 
```{r time}
dat_meting <- expand.grid(id = unique(dat_rename$id), meting = 1:5)
dat_long <- full_join(dat_rename, dat_meting)
```

The following step recodes the measurement occasions into months and adds a quadratic term 
```{r time2}
dat_long %<>%
  mutate(meting_mnd = recode_factor(meting, 
                                    `1` = "0", 
                                    `2` = "3", 
                                    `3` = "7", 
                                    `4` = "12", 
                                    `5` = "17") %>% 
           as.character() %>% as.numeric(),
         meting_squared = meting_mnd * meting_mnd)
```

---

## Add the occupation of participants

First recode `isco` to `oesch`
```{r work}
oesch <- read_excel("oesch.xlsx")
dat_oesch <- dat_long %>% 
  mutate(isco08 = as.character(isco08))
dat_oesch$oesch <- mapvalues(dat_oesch$isco08, 
                             from = oesch$ISCO, 
                             to = oesch$OESCH)
```

Then clean the `oesch` codes and make the empty cells for occupation explicitly NA
```{r work2}
dat_clean <- dat_oesch %>% 
  zap_labels() %>% 
  select(-isco08, -weegfactor) %>% 
  mutate(oesch = na_if(oesch, 99),
         oesch = na_if(oesch, 110),
         oesch = na_if(oesch, 310),
         oesch = na_if(oesch, 4111),
         oesch = na_if(oesch, 7536))
dat_clean$oesch[dat_clean$oesch == ""] <- NA
```

---

## Combine health status question into a single variable
```{r health}
dat_clean$q43 <- rowMeans(data.frame(dat_clean$q43_wave1, dat_clean$q43_wave2tot5), na.rm = TRUE)
dat_clean[sapply(dat_clean, is.nan)] <- NA
```

---

## Select relevant variables

Create variable vectors for imputation models
```{r variables}
vars_outcome <- c("q60_1", "q49_1", "q49_2", "q49_3", "q49_4", "q49_5", "q49_6")
vars_fixed <- c("edu", "oesch", "geboortejaar", "q29", "q52", "q53", "q54", "sekse", "etn_herkomst")
vars_random <- c("meting_mnd", "meting_squared", "q43", "q48_1", "q48_9", "q48_10", "q48_11", "q48_12", "q47_1", "q47_2", "q47_3", "q33_1", "q33_2", "q33_3", "q33_4", "q33_5", "q33_6")
vars_covariates <- c("q34_1", "q34_2", "q34_3", "q34_4", "q34_5", "q38_1", "q38_2", "q38_3", "q38_4", "q31_1", "q31_2", "q31_3", "q31_4", "q31_5", "q31_6", "q31_7", "q59", "q60_2", "q60_3", "q60_4", "q60_8", "q60_10", "q60_12")
vars_analyse <- c("id", vars_outcome, vars_fixed, vars_random)
```

Filter the relevant variables
```{r filter}
# from the cleaned data, select the analysis variables and covariates
dat_clean <- dat_clean[c(vars_analyse, vars_covariates)]
vars <- names(dat_clean)
```

---

# Imputation

---

## Impute fixed variables
The following code takes the most frequent observation per participant across measurement occasions for variables that are assumed constant in the analysis model, and fills this value in for all measurement occasions 
```{r constants}
# calculate mode for constant variables
modi <- split(dat_clean[, c("id", vars_fixed)], factor(dat_clean$id)) %>% 
  map_dfr(~modus_per_column(.x)) %>% 
  mutate(across(everything(), ~as.numeric(.x)),
         id = as.numeric(id))
# combine constants with the time-varying data
dat_imp <- dat_clean[, vars %nin% vars_fixed] %>% 
  left_join(modi, by = "id")
# check if the constants are in fact constant across measurements
dat_imp[1:200,] %>% 
  ggplot(aes(x = meting_mnd, y = edu, color = as.factor(id))) +
  geom_line() +
  theme(legend.position = "none")
```

---

## Develop imputation models
The minimum correlation between (incomplete) variables for inclusion in the imputation models is set to r = 0.1. The outcome variables (trust in the government and mental health during COVID) are imputed using multilevel predictive mean matching. The time-varying predictor variables and covariates are imputed using the so-called 'indicator method'. Variables that are assumed constant across measurement occasions in the analysis model (e.g. ethnicity) are imputed using cluster-level predictive mean matching.

First inspect missingness pattern and correlations
```{r plot}
md.pattern(dat_imp[vars_fixed], rotate.names = TRUE)
md.pattern(dat_imp[vars_outcome], rotate.names = TRUE)
md.pattern(dat_imp[vars_random], rotate.names = TRUE, plot = FALSE)
ggmice::plot_corr(dat_imp[vars_analyse], label = TRUE, square = FALSE, rotate = TRUE)
```

Then create vector of imputation methods
```{r methods}
vars <- names(dat_imp)
vars_complete <- vars[colSums(is.na(dat_imp)) == 0]
meth_imp <- mice::make.method(dat_imp)
meth_imp[vars %in% vars_fixed & vars %nin% vars_complete] <- "2lonly.pmm" #constante variablen
meth_imp[vars %in% vars_outcome] <- "2l.pmm"
meth_imp[vars %in% vars_random] <- "pmm"
#CHECK IF IMPS FOR VARS_FIXED REMAIN CONSTANT AFTER IMPUTATION. ELSE USE MODE AFTER IMP
```

And create predictor matrix for the imputation models
```{r pred}
pred_imp <- mice::quickpred(dat_imp, mincor = 0.1) #correlaties r >= 0.06
plot_pred(pred_imp)
# pred_imp[pred_imp == 1] <- 2 #vervang 1en door 2en vanwege conventies multilevelmodellen mice
pred_imp[, vars_outcome] <- 2 #uitkomst analysemodel als predictor voor alle variabelen
pred_imp[vars_outcome, ] <- 1 #alle variabelen als predictor voor uitkomst analysemodel
pred_imp[vars_random, "meting_mnd"] <- 2 #meetmoment als voorspeller voor varierende variabelen
pred_imp[vars_random, "meting_squared"] <- 2 #meetmoment als voorspeller voor varierende variabelen
pred_imp[vars_complete, ] <- 0 #volledig geobserveerd, dus verwijderen
pred_imp[, "id"] <- -2 #clustervariabele gespecificeerd in elk model
diag(pred_imp) <- 0 #variabelen niet als predictor voor zichzelf
plot_pred(pred_imp)
```

---

# Impute the data

Run a single iteration to check for errors
```{r impute}
imp <- mice(dat_imp, m = 10, maxit = 1, 
            method = meth_imp, 
            predictorMatrix = pred_imp, 
            printFlag= FALSE, 
            seed = 104,
            visitSequence = "monotone")
saveRDS(imp, "imp_1it.RDS")
```

Add iterations for imputation algorithm convergence
```{r impute2}
imp <- mice.mids(imp, maxit = 19, printFlag=FALSE)
saveRDS(imp, "imp_20it.RDS")
```
















