---
title: "Imputatie COVID data"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>



---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# set random number generator
set.seed(11)

# setup environment
library(tidyverse)  # All things useful
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(plyr)       # Data wrangling
library(magrittr)   # Pipes in R

# Define function for `not in`
`%nin%` <- Negate(`%in%`)
```

---

# Setup

Import the preprocessed data.
```{r data}
load("../Data/clean.Rdata")
```

Recode categorical variables for imputation.
```{r}
dat_clean <- dat_clean %>% 
  mutate(q29 = as.numeric(q29),
         edu = as.numeric(edu),
         etn_herkomst = as.numeric(etn_herkomst))
```


Load relevant variables.
```{r variables}
vars_outcome <- c("q60_1", "q49_1", "q49_2", "q49_3", "q49_4", "q49_5", "q49_6")
vars_fixed <- c("weegfactor", "edu", "age", "q29", "q52", "q53", "q54", "sekse", "etn_herkomst")
vars_random <- c("meting_mnd", "meting_squared", "q43", "q48_1", "q48_9", "q48_10", "q48_11", "q48_12", "q47_1", "q47_2", "q47_3", "q33_1", "q33_2", "q33_3", "q33_4", "q33_5", "q33_6")
vars_covariates <- c("q34_1", "q34_2", "q34_3", "q34_4", "q34_5", "q38_1", "q38_2", "q38_3", "q38_4", "q31_1", "q31_2", "q31_3", "q31_4", "q31_5", "q31_6", "q31_7", "q59", "q60_2", "q60_3", "q60_4", "q60_8", "q60_10", "q60_12")
vars_analyse <- c("id", vars_fixed, vars_outcome, vars_random)
```

---

# Missing data

---


## Inspect missingness over time

The following code converts the data into 'wide format', where each row represents one respondent, and time-varying variables are repeated measurements over several columns. This allows us to evaluate the missing data pattern in the outcome variable (q60_1) over the time in months (q60_1m0 through q60_1m17).

```{r wide}
dat_wide <- dat_clean %>% 
  pivot_wider(id_cols = c("id", vars_fixed), values_from = c(vars_outcome, vars_random, vars_covariates), names_from = "meting_mnd", names_sep = "m")
plot_pattern(dat_wide[, c("q60_1m0", "q60_1m3", "q60_1m7", "q60_1m12", "q60_1m17")], square = FALSE)
patterns <- md.pattern(dat_wide[, c("q60_1m0", "q60_1m3", "q60_1m7", "q60_1m12", "q60_1m17")], plot = FALSE)
n_obs <- sum(as.numeric(row.names(patterns)[patterns[, ncol(patterns)] < 4]))
```

Out of the `r nrow(dat_wide)` respondents, `r n_obs` have observed data on the outcome variable for at least two time points.

---

## Develop imputation models

The minimum correlation between (incomplete) variables for inclusion in the imputation models is set to r = 0.1. The outcome variables (trust in the government and mental health during COVID) are imputed using multilevel predictive mean matching. The time-varying predictor variables and covariates are imputed using the so-called 'indicator method'. Variables that are assumed constant across measurement occasions in the analysis model (e.g. ethnicity) are imputed using cluster-level predictive mean matching.

First inspect missingness pattern and correlations
```{r plot}
md.pattern(dat_clean[vars_fixed], rotate.names = TRUE)
md.pattern(dat_clean[vars_outcome], rotate.names = TRUE)
md.pattern(dat_clean[vars_random], rotate.names = TRUE, plot = FALSE)
ggmice::plot_corr(dat_clean[vars_analyse], label = TRUE, square = FALSE, rotate = TRUE)
```

Then create vector of imputation methods
```{r methods}
vars <- names(dat_clean)
vars_complete <- vars[colSums(is.na(dat_clean)) == 0]
meth <- mice::make.method(dat_clean)
meth[vars %in% vars_fixed & vars %nin% vars_complete] <- "2lonly.pmm" #constante variablen
meth[vars %in% vars_outcome] <- "2l.pmm"
meth[vars %in% vars_random] <- "pmm"
#CHECK IF IMPS FOR VARS_FIXED REMAIN CONSTANT AFTER IMPUTATION. ELSE USE MODE AFTER IMP
```

And create predictor matrix for the imputation models
```{r pred}
pred <- mice::quickpred(dat_clean, mincor = 0.1) #correlaties r >= 0.06
plot_pred(pred, rotate = TRUE, label = FALSE)
# pred_imp[pred_imp == 1] <- 2 #vervang 1en door 2en vanwege conventies multilevelmodellen mice
pred[, vars_outcome] <- 2 #uitkomst analysemodel als predictor voor alle variabelen
pred[vars_outcome, ] <- 1 #alle variabelen als predictor voor uitkomst analysemodel
pred[vars_random, "meting_mnd"] <- 2 #meetmoment als voorspeller voor varierende variabelen
pred[vars_random, "meting_squared"] <- 2 #meetmoment als voorspeller voor varierende variabelen
pred[vars_complete, ] <- 0 #volledig geobserveerd, dus verwijderen
pred[, "id"] <- -2 #clustervariabele gespecificeerd in elk model
pred[, "weegfactor"] <- 0 #weights not used in imputation
diag(pred) <- 0 #variabelen niet als predictor voor zichzelf
plot_pred(pred, method = meth, rotate = TRUE, label = FALSE)
```

---


# Impute the data

Run a single iteration to check for errors. TODO: convert factors back to numeric.
```{r impute}
imp <- mice(dat_clean, m = 10, maxit = 1, 
            method = meth, 
            predictorMatrix = pred, 
            printFlag= FALSE, 
            seed = 104,
            visitSequence = "monotone")
saveRDS(imp, "../Data/imp_1it.RDS")
```

Add iterations for imputation algorithm convergence
```{r impute2}
imp <- mice.mids(imp, maxit = 19, printFlag=FALSE)
saveRDS(imp, "../Data/imp_20it.RDS")
```
















