---
title: "Preprocessing"
author: "Hanne Oberman"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Packages and functions used
```{r setup, include=TRUE, message=FALSE, warning=TRUE}
# setup environment
library(haven)      # For importing SPSS data
library(tidyverse)  # All things useful
library(psych)      # For descriptive statistics
library(mice)       # For incomplete data analysis
library(miceadds)   # Additions to mice
library(ggmice)     # Plotting device for mice
library(lme4)       # Linear mixed-effect modeling
library(plyr)       # Data wrangling
library(magrittr)   # Pipes in R

# Define function for `not in`
`%nin%` <- Negate(`%in%`)

# Define function to compute the mode of a vector
modus <- function(x) {
  tally <- table(x, useNA = "no")
  if(dim(tally)==0) {
    mode <- NA
    } else {
      mode <- names(which.max(tally))
      }
  return(as.numeric(mode))
}

# Define function to compute the mode of several columns
modus_per_column <- function(x) {
  apply(x, 2, modus)
}
```

---

# Import and inspect the data

--- 

The SPSS formatted data is loaded into `R`.
```{r data}
dat_raw <- read_sav("../Data/data_correctlycoded_GV.zsav") %>% zap_labels()
```

Calculate descriptive statistics.
```{r desc}
psych::describe(dat_raw, fast = TRUE)
```

Rename labels and remove attributes.
```{r rename}
# clean names
dat_rename <- janitor::clean_names(dat_raw) 
# strip attributes
dat_rename[] <- lapply(dat_rename, as.vector)
```


---

# Data editing

---

## Recode measurement occasions

Make time dimension consistent and add polynomial for measurement occasion. The following step adds non-observed measurement occasions when participants do not have all measurement occasions observed. 
```{r time}
dat_meting <- expand.grid(id = unique(dat_rename$id), meting = 1:5)
dat_long <- full_join(dat_rename, dat_meting)
```

The following step recodes the measurement occasions into months and adds a quadratic term.
```{r time2}
dat_long %<>%
  mutate(
    meting_mnd = recode_factor(
      meting,
      `1` = "0",
      `2` = "3",
      `3` = "7",
      `4` = "12",
      `5` = "17"
    ) %>%
      as.character() %>% as.numeric(),
    meting_squared = meting_mnd * meting_mnd
  )
```

---

## Recode health status

Combine the two health status questions into a single variable.
```{r health}
dat_long$q43 <- rowMeans(data.frame(dat_long$q43_wave1, dat_long$q43_wave2tot5), na.rm = TRUE) 
dat_long[sapply(dat_long, is.nan)] <- NA 
```

---

## Fill in observed demographics

Demographic variables are assumed to be fixed over measurement occasions within respondents. Therefore, we can fill in missing demographics based on observed measurements. The following code takes the most frequent observation per participant across measurement occasions for variables that are assumed constant in the analysis model, and fills this value in for all measurement occasions.
```{r constants}
# calculate mode for constant variables
modi <-
  split(dat_long[, c(
    "id",
    "weegfactor",
    "edu",
    "geboortejaar",
    "q29",
    "q52",
    "q53",
    "q54",
    "sekse",
    "etn_herkomst"
  )], factor(dat_long$id)) %>%
  map_dfr( ~ modus_per_column(.x)) %>%
  mutate(across(everything(), ~ as.numeric(.x)),
         id = as.numeric(id))
# combine constants with the time-varying data
dat_demo <-
  dat_long[, names(dat_long) %nin% c(
    "weegfactor",
    "edu",
    "geboortejaar",
    "q29",
    "q52",
    "q53",
    "q54",
    "sekse",
    "etn_herkomst"
  )] %>%
  left_join(modi, by = "id")
```

---

## Recode demographic variables

Combine smaller household categories into one 'other'.
```{r household}
dat_demo$q29[dat_demo$q29 == 6] <- 5
dat_demo$q29[dat_demo$q29 == 7] <- 5
dat_demo <- dat_demo %>% mutate(
  q29 = as.factor(q29)
)
levels(dat_demo$q29)<- c("Alleenstaand zonder kinderen", 
                     "Alleenstaand met kinderen", 
                     "Samenwonend met partner met thuiswonende kinderen",
                     "Samenwonend met partner zonder thuiswonende kinderen", 
                     "Anders")
```

Combine education levels into three names categories.
```{r edu}
dat_demo$edu[dat_demo$edu < 4] <- 1
dat_demo$edu[dat_demo$edu == 4 | dat_demo$edu == 5] <- 2
dat_demo$edu[dat_demo$edu > 5] <- 3
dat_demo <- dat_demo %>% mutate(
  edu = as.factor(edu)
)
levels(dat_demo$edu)<- c("Hoog", "Middel", "Laag")
```

Label factor levels for sex and ethnic background.
```{r sex}
dat_demo$sekse <- as.factor(dat_demo$sekse)
levels(dat_demo$sekse) <- c("Man", "Vrouw")
dat_demo$etn_herkomst <- as.factor(dat_demo$etn_herkomst)
levels(dat_demo$etn_herkomst)<- c("Nederlandse achtergrond", 
                              "Westerse migratieachtergrond", 
                              "Niet-westerse migratieachtergrond")
```

Compute age at time point 1.
```{r age}
dat_demo <- dat_demo %>% mutate(
  age = 2020-geboortejaar
)
```


---

# Select and save clean data

---

Group relevant variables together for further analysis.
```{r variables}
vars_outcome <- c("q60_1", "q49_1", "q49_2", "q49_3", "q49_4", "q49_5", "q49_6")
vars_fixed <- c("weegfactor", "edu", "age", "q29", "q52", "q53", "q54", "sekse", "etn_herkomst")
vars_random <- c("meting_mnd", "meting_squared", "q43", "q48_1", "q48_9", "q48_10", "q48_11", "q48_12", "q47_1", "q47_2", "q47_3", "q33_1", "q33_2", "q33_3", "q33_4", "q33_5", "q33_6")
vars_covariates <- c("q34_1", "q34_2", "q34_3", "q34_4", "q34_5", "q38_1", "q38_2", "q38_3", "q38_4", "q31_1", "q31_2", "q31_3", "q31_4", "q31_5", "q31_6", "q31_7", "q59", "q60_2", "q60_3", "q60_4", "q60_8", "q60_10", "q60_12")
vars_analyse <- c("id", vars_fixed, vars_outcome, vars_random)
```

Filter the relevant variables.
```{r filter}
dat_clean <- dat_demo[c(vars_analyse, vars_covariates)] # select the analysis variables and covariates
```

Save the data.
```{r clean}
save(dat_clean, file = "../Data/clean.Rdata")
```


